---
title: "GitHub branches using RStudio"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Is your fav' iconic !?!

Write and R script to compare the csv with your favorite desserts you modified previously with the top 42 most iconic American desserts 

1. Clone the repository you just created to Taylor
2. Create a new branch using RStudio and name it `myinitials_rstudio`
3. Start a new script named `desserts_match_myinitials.R` 
4. As pair programming, write a script should read a csv file of your favorite dessert (create it if you do not have one yet) and the csv file with the most iconic desserts (see link below) into R and try to determine if your favorite dessert is part of the [most iconic desserts](https://www.eatthis.com/iconic-desserts-united-states/)!

You can download the iconic data here: <https://github.com/brunj7/EDS-214-analytical-workflows/blob/main/data/iconic_desserts.csv?raw=TRUE>

## Note

Here is how we created the iconic listing

```{r getting the data, eval=FALSE}
library(tidyverse)
library(rvest)

# read the webpage code
webpage <- read_html("https://www.eatthis.com/iconic-desserts-united-states/")

# Extract the desserts listing
dessert_elements<- html_elements(webpage, "h2")
dessert_listing <- dessert_elements %>% 
  html_text2() %>% # extracting the text associated with this type of elements of the webpage
  as_tibble() %>% # make it a data frame
  rename(dessert = value) %>% # better name for the column
  head(.,-3) %>% # 3 last ones were not desserts 
  rowid_to_column("rank") %>% # adding a column using the row number as proxy for the rank
  write_csv("data/iconic_desserts.csv") # save it as csv

```

